First Measurements of the D(e,e'p)n Cross Section at \\ Very High Recoil Momenta and Large Q^{2}

### 2019-12-17 MY_PUBLICATIONS/PRL/draft_v2/body.tex
update

model. The ratio of data to simulation yield was determined to be $97.6\pm0.3 \%$. For $^{2}H(e,e'p)n$, the low missing momentum data ($p_{r}=80$ MeV/c) were compared to the Hall A data (See Fig. \ref{fig:fig1}).

@@

dominant and all models exhibit a similar behaviour which obscures any possibility of extracting the momentum distributions at these angles. At smaller recoil angles, $\theta_{nq}=35^{o}$ and $45^{o}$ shown in
Figs. \hyperref[fig:fig1]{1(a)} and \hyperref[fig:fig1]{1(b)}, all models are sensitive to momentum distributions to some extent beyond $300$ MeV/c before FSIs start to appear. The Paris and AV18 calculations
exhibit a similar behaviour in the momentum distributions as opposed to the CD-Bonn calculation, where FSIs start to show up earlier than the other models predict.

@@

deuteron momentum distribution calculated using the charge-dependent Bonn (CD-Bonn) potential\cite{PhysRevC.63.024001}. The theoretical calculations for the CD-Bonn and Argonne $v_{18}$ (AV18)\cite{PhysRevC.51.38}
potentials were performed by M. Sargsian\cite{PhysRevC.82.014612} and those for the Paris potential\cite{PhysRevC.21.861} were done by J.M. Laget\cite{LAGET2005}.

@@

Hall A data, however, shows excellent agreement with the Paris FSI. For $p_{r}<300$ MeV/c, FSIs are small as indicated by the approximate ratio R$\sim$1 for all the theoretical calculations using FSI, which the data follows. The
small dip observed in this region (R$<1$) is indicative of the approximate cancellation between the PWIA/FSI interference (screening term) and the modulus-squared of FSI (re-scattering) terms in the cross section. \\

@@

The data is clearly sensitive to the momentum distributions using the CD-Bonn calculations and show an earlier rise than predicted by theory, a behaviour which is not described by any of the models. \\

@@

transitioning ($R>1$) to other models. \\ 
\indent The $\theta_{nq}=35^{o}$ [Fig. \hyperref[fig:fig2]{2(a)}] is clearly the optimal kinematics to study the high momentum components of the deuteron wavefunction, as the data is sensitive to momentum

@@

\indent This commissioning experiment extended the previous Hall A cross section measurements on the $^{2}H(e,e'p)n$ reaction to 

@@

The experimental reduced cross sections were extracted and found to be best described by M. Sargsian's calculations using the CD-Bonn potential with sensitivity to the momentum distributions
up to $p_{r}\sim580$ and $750$ MeV/c for $\theta_{nq}\sim45^{o}$ and $35^{o}$, respectively before the data transitioning to other theoretical models, which is a
behavior that was not predicted by any of the models. The early transition observed in both the 35 ad 45 degrees kinematic settings gives a hint that 
there might be additional degrees of freedom (transition to quark-gluon degrees of freedom) that might not be accounted for in NN potentials presented. \\
\indent However, given that this experiment ran for only 6 out of the 42 days (21 PAC days assuming 100$\%$ beam efficiency) of beam time and 3 out of the 8 kinematic settings approved in
the original proposal\cite{e12_10_003_proposal}, additional beam time would be required to measure the full kinematic coverage (more missing momentum settings) to gain the necessary statistics 
in order to make any definitive arguments about the underlying physics observed. \\
\indent We acknowledge the outstanding support of the staff of the Accelerator and Physics Divisions at Jefferson Lab
as well as the entire Hall C staff, technicians, graduate students and users who took shifts or contributed
to the equipment for the Hall C upgrade making all four commissioning experiments possible.

>>>>

model. The ratio of data to simulation yield was determined to be $97.6\pm0.3 \%$ (statistical uncertainty only). For $^{2}H(e,e'p)n$, the low missing momentum data ($p_{r}=80$ MeV/c) were compared to the Hall A data (See Fig. \ref{fig:fig1}).

@@

dominant and exhibit a similar behaviour among all models which obscures any possibility of extracting the momentum distributions at these angles. At smaller recoil angles, $\theta_{nq}=35^{o}$ and $45^{o}$ 
[Figs. \hyperref[fig:fig1]{1(a), 1(b)}], the Paris and AV18 calculations show sensitivity to momentum distributions and are within good agreement whereas the CD-Bonn calculation exhibits
a different behaviour beyond $p_{r}\sim$300 MeV/c which indicates a larger sensitivity to the different NN-potentials at higher missing momenta.

@@

deuteron momentum distribution calculated using the charge-dependent Bonn (CD-Bonn) potential\cite{PhysRevC.63.024001}.

@@

Hall A data, however, shows excellent agreement with the Paris FSI. For $p_{r}<300$ MeV/c, FSIs are small as indicated by the approximate ratio R$\sim$1 for all the theoretical calculations using FSI, which the
data follows. The small dip observed in this region (R$<1$) is indicative of the approximate (not exact) cancellation between the PWIA/FSI interference (screening term) and the modulus-squared of FSI (re-scattering) terms in
the cross section. \\

@@

The data agrees well with the CD-Bonn PWIA calculation but show an earlier rise than predicted by the CD-Bonn FSI, a behaviour which is not described by any of the models. \\

@@

exhibiting an earlier rise than predicted by CD-Bonn FSI. \\ 
\indent The $\theta_{nq}=35^{o}$ [Fig. \hyperref[fig:fig2]{2(a)}] appears to be the optimal kinematics to study the high momentum components of the deuteron wavefunction, as the data is sensitive to momentum

@@

\indent This experiment extended the previous Hall A cross section measurements on the $^{2}H(e,e'p)n$ reaction to 

@@

The experimental reduced cross sections were extracted and found to be in good agreement with the Hall A data. Furthermore, the CD-Bonn calculations
were found to be sensitive to momentum distributions up to $p_{r}\sim800$ MeV/c for recoil angles $\theta_{nq}=35\pm5^{o}$, which the data agreed
up to $p_{r}\sim750$ MeV/c. At higher missing momentum, however, all models are unable to describe the data, which is currently not well understood.
Given that this is a commissioning experiment that ran

\indent However, given that this experiment ran for only 6 out of the 42 days (21 PAC days assuming 100$\%$ beam efficiency) of beam time and 3 out of the 8 kinematic settings approved in
the original proposal\cite{e12_10_003_proposal}, additional beam time would be required to measure the full kinematic coverage (more missing momentum settings) to gain the necessary statistics 
in order to make any definitive arguments about the underlying physics observed. \\

\indent We acknowledge the outstanding support of the staff of the Accelerator and Physics Divisions at Jefferson Lab
as well as the entire Hall C staff, technicians, graduate students and users who took shifts or contributed
to the equipment for the Hall C upgrade making all four commissioning experiments possible.
